\cvsection{MUSIC VIDEOS}

% \cvsubsection{Choreographer}

\begin{cvhonors}
\cvhonor {Shakira ``Hips Don't Lie", Winner of MTV Video Music Award for Best Choreography in 2006}{}{Dir. Sophie Muller}{2006}
\cvhonor {Gwen Stefani ft. Akon ``Sweet Escape"}{}{Dir. Joseph Kahn}{2007}
\cvhonor {Gwen Stefani ``Wind It Up"}{}{Dir. Sophie Muller}{2006}
\cvhonor {Gwen Stefani ``Serious"}{}{Dir. Sophie Muller}{2005}
\cvhonor {Gwen Stefani ``Luxurious"}{}{Dir. Sophie Muller}{2005}
\cvhonor {Gwen Stefani ft. Eve ``Rich Girls"}{}{Dir. David LaChapelle}{2004}
\cvhonor {Katy Perry ``Hot N Cold"}{}{Dir. Alan Ferguson}{2008}
\cvhonor {Mariah Carey ft. Da Brat, Missy Elliott ``Heartbreaker (Remix)"}{}{Dir. Diane Martel}{1999}
\cvhonor {Jane Zhang ``Personal Look"}{}{Dir. Muh Chen}{2011}
\cvhonor {P. Diddy ft. Mase \& Biggie Smalls ``Mo Money Mo Problems"}{}{Dir. Hype Williams}{1997}
\cvhonor {Christina Milian ``AM to PM"}{}{Dir. Dave Meyers}{2001}
\cvhonor {Busta Rhymes ``Put Your Hands Where My Eyes Could See"}{}{Dir. Hype Williams}{1997}
\cvhonor {Aaliyah ``Four Page Letter"}{}{Dir. Daniel Pearl}{1997}
\cvhonor {Aaliyah ``Hot Like Fire"}{}{Dir. Lance ``Un" Rivera}{1997}
\cvhonor {Mýa ft. Lil Wayne ``Lock You Down"}{}{Dir. Benny Boom}{2007}
\cvhonor {Mýa ``The Best of Me"}{}{Dir. Chris Robinson}{2000}
\cvhonor {Salt N Pepa ``Gitty Up"}{}{Dir. Paul Hunter}{1998}
\cvhonor {Ginuwine ``In Those Jeans"}{}{Dir. Chris Robinson}{2003}
\cvhonor {Lil' Kim ``Crush On You"}{}{Dir. Lance ``Un" Rivera}{1997}
\cvhonor {Musiq Soulchild ``Forthenight"}{}{Dir. Bryan Barber}{2003}
\cvhonor {Foxy Brown ft. Dru Hill ``Big Bad Mama"}{}{Dir. Joseph Kahn}{1997}
\cvhonor {Black Eyed Peas ``Pump It"}{}{Dir. Francis Lawrence}{2006}
\cvhonor {Wyclef Jean ``It Doesn't Matter"}{}{Dir. Hype Williams}{2000}

\cvhonor {Bob Sinclair ft. Sugarhill Gang ``Lala Song"}{}{Dir. Denis Thybaud}{2009}
% \cvhonor {Danya ``Ellelah Ashofak"}{}{Dir. Muh Che}{??}
\cvhonor {Gnarls Barkley ``Going On"}{}{Dir. Wendy Morgan}{2008}
\cvhonor {Colby O'Donis ft. Akon ``What You Got"}{}{Dir. Gil Green}{2008}
\cvhonor {Gnarls Barkley ``Go-go Gadget Gospel"}{}{Dir. Robert Hales}{2007}
% \cvhonor {Silkk The Shocker ft. Mýa ``Somebody Like Me"}{}{Dir. Chris Robinson}{1999}
\cvhonor {Mýa ft. Silkk The Shocker ``Movin' On"}{}{Dir. Little X}{1998}
\cvhonor {The Cheetah Girls ``Shake Your Tailfeather"}{}{Dir. Chris Alender}{2006}
\cvhonor {Beverley Knight ``Shape of You"}{}{Dir. Max \& Dania}{2002}
\cvhonor {Jagged Edge ft. Nas ``I Got It 2"}{}{Dir. Bryan Barber}{2002}
\cvhonor {Nivea ``Don't Mess With the Radio"}{}{Dir. Chris Robinson}{2001}
\cvhonor {3LW ``Playa Gon' Play"}{}{Dir. Darren Grant}{2001}

\end{cvhonors}


% remove
% \cvhonor {t.A.T.u ``220"}{}{Dir. James Cox}{2008}
% \cvhonor {Meital Dohan ``??"}{}{Dir. ??}{??}
% \cvhonor {Jordyn Taylor ``Accessory"}{}{Dir. R Malcolm Johns}{??}
% \cvhonor {Kaci Brown ``Instigator"}{}{Dir. Vem}{2006}