\cvsection{TELEVISION}

\cvsubsection{Choreographer}
\begin{cvhonors}

\cvhonor {2010 MTV Movie Awards}{Katy Perry performance}{MTV}{2010}
\cvhonor {2010 MuchMusic Video Awards}{Katy Perry ``California Girls" performance}{MuchMusic}{2010}
\cvhonor {So You Think You Can Dance. Season 2}{}{FOX/Dir. Nigel Lythgoe}{2009}
\cvhonor {So You Think You Can Dance Canada. Seasons 1-4}{}{CTV}{2008-2011}
\cvhonor {Macy’s Thanksgiving parade}{Harajuku Lovers performance}{NBC}{2008}
\cvhonor {Dancing With the Stars}{}{ABC/Dir: Alex Rudzinski}{2008}
\cvhonor {Dance On Sunset}{Colby O'Donis \& Akon performance}{Nickelodeon}{2008}
\cvhonor {Dick Clark's New Year's Rockin' Eve}{Sean Kingston performance}{NBC}{2008}
\cvhonor {America’s Got Talent}{Sean Kingston performance}{NBC}{2007}
\cvhonor {Kid's Choice Awards}{Gwen Stefani performance}{FOX}{2006}
\cvhonor {American Idol}{Gwen Stefani performance}{FOX}{2007}
\cvhonor {Jimmy Kimmel Live}{Gwen Stefani performance}{ABC/Dir. Andy Fisher}{2008}
\cvhonor {American Music Awards}{Gwen Stefani performance}{ABC/Dir. Louis J. Horvitz}{2006}
\cvhonor {Billboard Awards}{Gwen Stefani performance}{FOX/Dir. Bruce Gowers}{2006}
\cvhonor {Saturday Night Live}{Gwen Stefani performance}{NBC}{2008}
\cvhonor {Teen Choice Awards}{Gwen Stefani performance}{FOX}{2005}
\cvhonor {48th Annual Grammy Awards}{Gwen Stefani performance}{CBS/Dir. Walter C. Miller}{2005}
\cvhonor {3rd Annual TV Land Awards}{Mya performance}{TV Land}{2005}
\cvhonor {Brit Awards}{Gwen Stefani performance}{BBC}{2006}
\cvhonor {Billboard Awards}{Gwen Stefani performance}{FOX}{2007}
\cvhonor {European Music Awards}{Gwen Stefani performance}{MTV Europe}{2005}
\cvhonor {American Music Awards}{Gwen Stefani performance}{ABC}{2006}
% \cvhonor {Johnny Zero}{}{FOX}{??}
\cvhonor {30th Daytime Emmy Awards}{Wayne Brady performance}{CBS}{2003}
\cvhonor {2003 GQ "Men of the Year" Awards}{Mya performance}{TBS/Dir. Beth McCarthy-Miller}{2003}
\cvhonor {Today Show}{Jennifer Lopez performance}{NBC}{2003}
\cvhonor {Top of the Pops}{Jennifer Lopez performance}{BBC}{2001}
\cvhonor {2002 Soul Train Music Awards}{Jagged Edge performance}{WB/Dir. Morris Abraham}{2002}
\cvhonor {Soul Train}{Christina Milian performance}{WB}{2001}
\cvhonor {Orange Bowl's half-time show}{Christina Milian performance}{ABC}{2002}
\cvhonor {BET Tonight}{3LW performance}{BET}{2001}
\cvhonor {MTV's House of Style}{Mýa performance}{MTV}{1998}
\cvhonor {Motown Live}{Mýa performance}{WB/Dir. Terri McCoy}{1998}
\cvhonor {World Music Awards}{Mýa ``The Best of Me" performance}{}{2000}
% \cvhonor {Top of the Pops}{Mýa ``The Best of Me" performance}{}{???}
\cvhonor {NFL Pro Bowl}{Salt N Pepa ``Gitty Up" (and medley) performance}{}{1997}

\end{cvhonors}